Bibat: Batteries-include Bayesian Analysis Template

### 2024-04-10 paper/main.qmd
Add hello world example to paper

In order to use bibat, a user must first install the templating library copier
[@copierdevelopersCopier2024], then choose a directory name and run this command
from the command line:

```sh
$ copier copy gh:teddygroves/bibat my-chosen-directory-name
```

This command triggers an interactive form which prompts the user to select
a range of customisation options. The new directory will then be created
if necessary and filled with code that implements an example analysis, with
customisations reflecting the user's choices. This analysis works immediately,
and can be reproduced with the single command `make analysis` without the need
for any further action by the user: in this sense bibat comes with batteries
included.

@@

>>>>

To use bibat, a user must first install the templating library copier
[@copierdevelopersCopier2024] and then use the command `copier copy` to trigger
bibat. The user is then presented with an interactive form which prompts them
to select from a range of customisation options. A new directory is then created
if necessary and filled with code that implements an example analysis, with
customisations reflecting the user's choices. This analysis works immediately,
and can be reproduced with the single command `make analysis` without the need
for any further action by the user: in this sense bibat comes with batteries
included.

@@

# 'Hello world' example

This section illustrates bibat's use by stepping through a typical example.
A similar description can be found on the 'Getting started' page of bibat's
documentation.

The first step to use bibat is installing copier. This can be done using pipx
[@pipxdevelopersPipx2024] as follows:

```sh
$ pipx install copier
```

Next, choose a directory name, e.g. `hello-world` and call trigger bibat using
copier:

```sh
$ copier copy gh:teddygroves/bibat hello-world
```

Here is what should appear next. Some options are text fields, and others, such
as `open_source_license` are enumerated choices.

```sh
Welcome to bibat, the batteries-included Bayesian analysis template!

You'll be asked a series of questions whose answers will be used to
generate a tailored project for you.

🎤 Name of your project
   Hello world
🎤 Name of your project, with no spaces (used for venv and package names)
   hello_world
🎤 A short description of the project.
   A 'hello world example of using bibat'
🎤 Your name (or your organization/company/team)
   Hello world developers
🎤 Author email (will be included in pyproject.toml)
   author@email.com
🎤 Code of conduct contact
   author@email.com
🎤 open_source_license
   MIT
🎤 docs_format
   Quarto
🎤 create_dotgithub_directory (bool)
   Yes
```

After all the fields are completed, the directory `hello-world` is created if it
doesn't exist and populated or edited based on the form. If this is successful,
some more messages appear indicating which files have been created or edited and
explaining what to do next.

The final setup step is to change directory into the new folder and run `make analysis`:

```sh
$ cd hello-world
$ make analysis
```

This will set up a suitable Python virtual environment, install non-Python
dependencies if necessary and then run the analysis, creating the results shown
on the right-hand side of @fig-workflow.
